I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-23 Paper/proofs.tex
appendix

Before the proof of two theorems, we will prove a weaker version, that is, consider not only compensating pairs, but also pairs that allows common nodes (the two paths in a compensating pairs cannot have a common nodes). We may call such pair a weak compensating pair.

First, notice that if $\Val_{\vx}(b)$ is maximal (resp. minimal), 
then $\Val_{\boldsymbol{x}}(\hat{b})$ also gets maximal (resp. minimal).

For convenience, when we discuss about the maximal or minimal values for nodes $n$ in a network without risk of confusing, we will write $\max(n),\min(n)$ directly, which means $\max(\Val(n))$, $\min(\Val(n))$ or $\max_{\vx}(\Val_{\vx}(n)),\min_{\vx}(\Val_{\vx}(n))$.

@@

\begin{definition}[Sign of Node]\label{sign_of_nodes}
	We define the partial sign function $S$ on neurons $n$: 	
	\begin{enumerate}
		\item $S(n)=0$ if all path from $n$ to $z$ have 0 weight; 
		\item $S(n)=1$ if all path from $n$ to $z$ have non-negative weight, and at least one path has a positive weight; 
		\item $S(n)=-1$ if all path from $n$ to $z$ have non-positive weight, and at least one path has a negative weight. 
	\end{enumerate}
\end{definition}

In general, $S$ may not be defined on every node (e.g. if there is a negative and a positive path from $a$ to $c$). However, if there is no compensating pair, $S$ is defined on all nodes: any node fulfills one of above cases (1),(2),(3).
For instance, for an input node $a_i$ of any 3 layer DNN:
\begin{enumerate}
	\item  $S(a_i)=0$ if 
	for all $b_j, W_{a_i b_j}\cdot W_{b_j c} = 0$

@@

@@

				Second, we show that if neither 1 nor 2 hold, then $b$ will be in a weak compensating path.
				Because 2) does not hold, there exists $j \in J$ with $weight({a_j,b}) \neq 0$, say $>0$.
				Because 1) does not hold, $weight({b,z}) \neq 0$, say $>0$.
				Now, by definition of $J$, there is a pair of weak compensating paths $\pi,\pi'$ 
				from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
				Then two paths $(a_j,b,z)$ and $\pi'$ also form a weak compensating pair. \qed
			\end{proof}

>>>>

\section*{Appendix}
As a first step to prove Theorems \ref{th1},\ref{th2}, 
we will relax the compensating pairs notion to allows pairs of paths having nodes in common.
Such a pair is called a {\em weak compensating pair}.
We will then in a second step prove Theorems \ref{th1},\ref{th2} for the full definition of compensating pairs of paths.

First, notice that if $\Val_{\vx}(b)$ is maximal (resp. minimal), 
then $\Val_{\boldsymbol{x}}(\hat{b})$ also gets maximal (resp. minimal). 
For convenience, when we discuss about the maximal or minimal values for nodes $n$ in a network without risk of confusing, 
we will write $\max(n)$ to denote $\max(\Val_{\vx}(n))$, and $\min(n)$ to denote $\min(\Val_{\vx}(n))$.

@@

\begin{definition}[Sign of Node]\label{sign_of_nodes}
	We define the partial sign function $S$ on node $n$: 	
	\begin{enumerate}
		\item $S(n)=0$ if all path from $n$ to $z$ have weight $0$; 
		\item $S(n)=1$ if all path from $n$ to $z$ have non-negative weight, and at least one path has a positive weight; 
		\item $S(n)=-1$ if all path from $n$ to $z$ have non-positive weight, and at least one path has a negative weight. 
	\end{enumerate}
\end{definition}

In general, $S$ may not be defined on every node 
(e.g. if there is a negative and a positive path from $a$ to $c$). 
However, if there is no compensating pair of paths, 
$S$ is defined on all nodes: any node fulfills one of above cases (1),(2),(3).

For instance for any 3 layer DNN: for an input node $a_i$:
\begin{enumerate}
	\item  $S(a_i)=0$ if 
	for all $b_j, W_{a_i b_j}\cdot W_{b_j c} = 0$

@@

Assume that there is a no (weakly) compensating pair of paths.

@@

				Second, we show that if neither 1 nor 2 hold, then $b$ will be in a weak compensating path.
				Because 2) does not hold, there exists $a_j \in J$ with $weight({a_j,b}) \neq 0$, say $>0$.
				Because 1) does not hold, $weight({b,z}) \neq 0$, say $>0$.
				Now, by definition of $J$, there is a pair of weak compensating paths $\pi,\pi'$ 
				from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
				Then two paths $(a_j,b,z)$ and $\pi'$ also form a weak compensating pair. \qed
			\end{proof}
